%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV for A4 paper format
% XeLaTeX Template
% Version 1.1
%
% A4 version author:
% Marvin Frommhold (depressiverobot.com)
% https://github.com/depressiveRobot/friggeri-cv-a4
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Options
% 'print': remove colors from this template for printing
% 'nocolors' to disable colors in section headers
\documentclass[]{friggeri-cv-a4}

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications


\begin{document}
\header{andre}{melo}{software engineer} 

%----------------------------------------------------------------------------------------
% SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Belo Horizonte, Brazil
~
+55 (31) 99228 2842
~
\href{mailto:andrepontes@gmail.com}{andrepontes@gmail.com}
\href{http://github.com/andrepontesmelo}{github://andrepontesmelo}
\href{http://linkedin.com/in/andrepontesmelo}{linkedin://andrepontesmelo}
\section{languages}
portuguese 
english
\section{programming}
{\color{red} $\varheartsuit$} C\#
javascript
bash
\end{aside}

%\section{intro}
%I am a software engineer that loves to design, test, implement and deploy complex distributed system. 
%Despite enjoying the design role as an architect, I also am passinate about coding as well as developing the tools and libraries that abstracts and  provide an easy way to use it.
%Currently looking forward to work in a diverse cultural environemnt in order to make the preexisting cloud computing state of art obsolete.

\section{experience}

\begin{entrylist}

\entry
{2017--Now}
{SEGFY}
{Belo Horizonte, Brasil}
{\emph{Software Engineer | Architect} \\

Development of .NET library that parse and translates legacy MS-AccessSQL into modern MySQL syntax, allowing the company's legacy code to run on upgraded database without massive code intervention.
Detailed achievements:
\begin{itemize}
    \item Reduction of 90\% in average query time.
    \item Reduction of massive concurrent access problems.
    \item Improved software latency by moving to AWS, using EC2, Lambda, API Gateway, Cloudwatch, DynamoDB and Beanstalk.
\end{itemize}}

\entry
{2013--NOW}
{INDÚSTRIA MINEIRA DE JOIAS}
{Belo Horizonte, Brazil}
{ Software development using .NET Framework for jewelry company.
\begin{itemize}
    \item Improved the worse business case that used to take two weeks to two days by automating and simplifing the company workflow. 
    \item Implemented bar code in reduced size tags using jewelry weight statistics for mapping.
\end{itemize}
}


%\entry
%{2012--2013}
%{GAP}
%{ San Francisco, USA (offshore)}
%{ Software development for fortune 500 client using agile methodology as offshore contractor.
%\begin{itemize}
    %\item Research and development that integrated functional tests to continuous integration pipeline using capybara-webkit headless driver.
%\end{itemize}
%}

\entry
{2011--2012}
{BLOOMINGDALE'S}
{New York, USA (offshore)}
{Software development for fortune 500 company using agile methodology.
\begin{itemize}
    \item Implemented UI for Bloomingdale's checkout project using javascript YUI and JSP.
\end{itemize}
}

\entry
{2010--2011}
{COTAK}
{Belo Horizonte, Brazil}
{ Development of a distributed computation of insurance quotes. Acquired experience in  distributed web systems, software architecture and technology research. 
Used C\# .NET and Amazon EC2 services. Had an opportunity to build an scheduler for a pair<algorithm, data> during runtime.
%  Built an autonomic library for configuring and logging distributed applications, and library for scheduling the execution of pair<algorithm, data> dynamically.
% Worked in development of a distributed computing cloud that automate UI web % interfaces, designed to feed automatic insurance quotes. Acquired experience in  distributed web systems, software architecture and technology research. Used C\# .NET and Amazon EC2 services. Had an opportunity to build an autonomic library for configure and log distributed applications, and a map reduce library for scheduling a set of pair<algorithm, data> dynamically.
\begin{itemize}
    \item Freed the customer machine by moving the execution of intensive cpu load from the customer machine to the cloud.
\end{itemize}
}


\end{entrylist}

\section{education}

\begin{entrylist}

\entry
{2013}
{Communication \& Interpersonal {\normalfont Skills Training}}
{Dale Carnegie Training}

\entry
{2004--2010}
{{\normalfont Bachelor of} Computer Science}
{Federal University of Minas Gerais, Brazil}

\entry
{2006}
{Article publication {\normalfont Color image enhancement through 2D histogram equalization}}
{Budapest, Hungary}

\end{entrylist}


\section{interests}

\textbf{professional:} software design, design patterns, distributed processing, automation, cloud, Copy on write filesystems. \textbf{personal:} piano, cooking

\end{document}
